Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach

### 2016-06-03 main.tex
change ti \citealias for K96 and T12

%\defcitealias{Hossein12}{T12}

\begin{document}
% TITLE
\defcitealias{Hossein12}{T12}

@@

% We used SOMs to classify SEDs of the galaxies with known morphological type from K96, and created networks with different usages.
% By varying size of networks, we found the relative similarity or dissimilarity between each type of galaxies.
% since we needed a 1D network with 22 neurons to be able to separate all the 12 types of galaxies from K96 for the first time, we concluded that types B and E, and types SB1 and SB2 galaxies are really similar to each other.
% We also showed that networks generated with SOM method can be used to easily identified new type of the galaxies or outlier, in large surveys.

% The sample of 142 high red-shift galaxies from T12 was used to test the trained networks.
% One of the main criteria to chose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
% The test results showed that using SOMs can lead us to identify galaxies with SEDs similar to two or more morphological types but not exactly the same as one of them.
% A freedom of having in between types is one of the main differences between supervised and unsupervised ANNs.
% T12  have used a supervised training method, and trained networks with K96 SED template.
% Same as this project, they tried to classify the sample of 142 galaxies using the trained networks.
% However, they could not classify 37 out of 142 galaxies in the sample.
% The unsupervised method that we used in this project, gave us the ability to classify galaxies either as one of the morphological types that have been introduced by K96 or between those types. 
% Therefore, we classified all 142 galaxies of our test sample.
% We plotted the properties of the galaxies in test sample using new classification and found a tighter correlations between mean values of age, sSFR, stellar mass, and extinction in FUV band of the galaxies in new classifications than previous studies.
% We also showed he properties of the galaxies in each groups is in good agreement between their morphological types.

@@

We used SOMs to classify the template spectra of K96, made from galaxies with known morphological type, and created networks with different uses.
By varying the size of the networks, we found the relative similarity between the K96 template classes.
A one-dimensional network with 22 neurons was needed in order to
separate all 12 K96 spectra; we concluded that K96 types B and E, and types SB1 and SB2, are very similar to each other.
We also showed that networks generated with the SOM method can be used to easily identify new types of spectra in large surveys.

A sample of 142 high red-shift galaxies from T12 was used to test the trained networks.
%One of the main criteria to choose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
The test results showed that using SOMs can allow identification of galaxies with SEDs similar to two or more morphological types.% but not exactly the same as one of them.
The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks.
T12 used a supervised training method to train networks with K96 SED templates and classify the same sample of 142 galaxy spectra;
however, they could not classify 37 out of 142 spectra.
The unsupervised method used in this project was able to classify  all 142 spectra in the sample
as belonging to one of the morphological types introduced by K96 or a class in between those types.

>>>>

%\defcitealias{Hossein12}{\citealias{Hossein12}}

\begin{document}
% TITLE
\defcitealias{Hossein12}{T12}
\defcitealias{Kinney96}{K96}

@@

% We used SOMs to classify SEDs of the galaxies with known morphological type from \citealias{Kinney96}, and created networks with different usages.
% By varying size of networks, we found the relative similarity or dissimilarity between each type of galaxies.
% since we needed a 1D network with 22 neurons to be able to separate all the 12 types of galaxies from \citealias{Kinney96} for the first time, we concluded that types B and E, and types SB1 and SB2 galaxies are really similar to each other.
% We also showed that networks generated with SOM method can be used to easily identified new type of the galaxies or outlier, in large surveys.

% The sample of 142 high red-shift galaxies from \citealias{Hossein12} was used to test the trained networks.
% One of the main criteria to chose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
% The test results showed that using SOMs can lead us to identify galaxies with SEDs similar to two or more morphological types but not exactly the same as one of them.
% A freedom of having in between types is one of the main differences between supervised and unsupervised ANNs.
% \citealias{Hossein12}  have used a supervised training method, and trained networks with \citealias{Kinney96} SED template.
% Same as this project, they tried to classify the sample of 142 galaxies using the trained networks.
% However, they could not classify 37 out of 142 galaxies in the sample.
% The unsupervised method that we used in this project, gave us the ability to classify galaxies either as one of the morphological types that have been introduced by \citealias{Kinney96} or between those types. 
% Therefore, we classified all 142 galaxies of our test sample.
% We plotted the properties of the galaxies in test sample using new classification and found a tighter correlations between mean values of age, sSFR, stellar mass, and extinction in FUV band of the galaxies in new classifications than previous studies.
% We also showed he properties of the galaxies in each groups is in good agreement between their morphological types.

@@

We used SOMs to classify the template spectra of \citealias{Kinney96}, made from galaxies with known morphological type, and created networks with different uses.
By varying the size of the networks, we found the relative similarity between the \citealias{Kinney96} template classes.
A one-dimensional network with 22 neurons was needed in order to
separate all 12 \citealias{Kinney96} spectra; we concluded that \citealias{Kinney96} types B and E, and types SB1 and SB2, are very similar to each other.
We also showed that networks generated with the SOM method can be used to easily identify new types of spectra in large surveys.

A sample of 142 high red-shift galaxies from \citealias{Hossein12} was used to test the trained networks.
%One of the main criteria to choose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
The test results showed that using SOMs can allow identification of galaxies with SEDs similar to two or more morphological types.% but not exactly the same as one of them.
The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks.
\citealias{Hossein12} used a supervised training method to train networks with \citealias{Kinney96} SED templates and classify the same sample of 142 galaxy spectra;
however, they could not classify 37 out of 142 spectra.
The unsupervised method used in this project was able to classify  all 142 spectra in the sample
as belonging to one of the morphological types introduced by \citealias{Kinney96} or a class in between those types.
